04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
working woohoo, had to delete some bad factors to get LD1 and LD2

# set levels
c.colData$treatment <- factor(c.colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9"))
levels(c.colData$treatment)
c.colData$sextissue <- as.factor(paste(c.colData$sex, c.colData$tissue, sep = "_"))

summary(c.colData[c(7,3,4,5,8)])

@@

```

@@

LDAanalysis <- function(mydds, mycolData){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform

@@

  mydata <- left_join(tvsd, mycolData, by = "V1")  # merge counts and variables

@@

  # LDA analysis
  # Fit the model
  model <- lda(treatment~ sex, data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)
  # Model accuracy
  mean(predictions$class==test.transformed$treatment)

@@

  # Predicted classes
  print(head(predictions$class, 6))
  # Predicted probabilities of class memebership.
  print(head(predictions$posterior, 6) )
  # Linear discriminants
  print(head(predictions$x, 3) )

  # LDA plot using ggplot2 
  lda.data <- cbind(train.transformed, predict(model)$x)
  p<-ggplot(data=lda.data, aes(x=treatment, y=LD1, fill = treatment)) +
    geom_bar( stat = "summary", fun.y = "mean")
  plot(p)

  # model accuracy 
  print(mean(predictions$class==test.transformed$treatment))
}

@@

LDAanalysis(dds.hypothalamus, colDataHyp)
LDAanalysis(dds.pituitary, colDataPit)
LDAanalysis(dds.gonad, colDataGon)
```

>>>>

# set levels
c.colData$treatment <- factor(c.colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9"))

c.colData$sextissue <- as.factor(paste(c.colData$sex, c.colData$tissue, sep = "_"))

@@

# drop columsn that are bad for model
c.colData$bird <- NULL
c.colData$tissue <- NULL
c.colData$study <- NULL
c.colData$group <- NULL
head(c.colData)
```

@@

LDAanalysis <- function(mydds, mycolData, mysubtitle){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform

@@

  mydata <- left_join(tvsd, mycolData, by = "V1")  # merge counts and variables
  mydata$V1 <- NULL

@@

  # LDA analysis
  # Fit the model
  model <- lda(hypothesis~ ., data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)
  # Model accuracy
  mean(predictions$class==test.transformed$hypothesis)

@@

  # Predicted classes
  head(predictions$class, 6)
  # Predicted probabilities of class memebership.
  head(predictions$posterior, 6) 
  # Linear discriminants
  head(predictions$x, 3)

  # LDA plot using ggplot2 
  lda.data <- cbind(train.transformed, predict(model)$x)
  p <- ggplot(data = lda.data, aes(LD1, LD2, color = hypothesis, shape = sex)) +
    geom_point() +
    labs(subtitle = mysubtitle)
  plot(p)

  # model accuracy 
  print(mean(predictions$class==test.transformed$hypothesis))
}

@@

LDAanalysis(dds.hypothalamus, colDataHyp, "Hypothalamus")
LDAanalysis(dds.pituitary, colDataPit, "Pituitary")
LDAanalysis(dds.gonad, colDataGon, "Gonad")
```
